Younger, Unmarried, Childless, and Less Happy Americans Use the Internet the Most

### 2023-03-16 outputs/paper/paper.qmd
Final edits to the quarto document - adding supplementary survey link in appendix

@@

Please find our supplementary survey to the GSS 2016 questionnaire at the following link: https://docs.google.com/forms/d/e/1FAIpQLSe0H6LMKnAehmWwiag4u4cBW27ttiRh_kY1SfmOc7pQWlNrrQ/viewform?usp=sf_link

>>>>

\newpage

@@

Please find our supplementary survey to the GSS 2016 questionnaire at the following footnote link.^[https://docs.google.com/forms/d/e/1FAIpQLSe0H6LMKnAehmWwiag4u4cBW27ttiRh_kY1SfmOc7pQWlNrrQ/viewform?usp=sf_link]

\newpage
